Higher-Order unification for free!

### 2024-05-13 paper/main.tex
typo

\noindent
However, this encoding has two big limitations. First it is
not always feasible to adopt it for Coq due to the fact that the type system
of the meta language is too limited to accommodate for the one the object language,
e.g. Coq can typecheck variadic functions~\cite{cpdt}. \\
Second, the encoding of Coq terms provided by Elpi is primarily used for meta
programming, i.e. to extend the Coq system. Consequently, it must be able to
manipulate terms that are not known in advance
without relying on introspection primitives such as Prolog's
\texttt{functor/3} and \texttt{arg/3}. To avoid that constants 
cannot be symbols of the meta language, but must rather
live in
an open world, akin to the \elpiIn{string} data type used in the \elpiIn{con}
constructor.

>>>>

\noindent
However, this encoding has two big limitations. First it is
not always feasible to adopt it for Coq due to the fact that the type system
of the meta language is too limited to accommodate for the one of the object language,
e.g. Coq can typecheck variadic functions~\cite{cpdt}. \\
Second, the encoding of Coq terms provided by Elpi is primarily used for meta
programming, i.e. to extend the Coq system. Consequently, it must be able to
manipulate terms that are not known in advance
without relying on introspection primitives such as Prolog's
\texttt{functor/3} and \texttt{arg/3}. To avoid that constants 
cannot be symbols of the meta language, but must rather
live in
an open world, akin to the \elpiIn{string} data type used in the \elpiIn{con}
constructor.
